Untitled

### 2023-09-09 code/analysis_Redo.Rmd
moving around heterogeneity analysis

plot.profit

did2s(
      data = df.profit %>% filter(!is.na(pc)) %>% mutate(pc = pc * 10 ), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )
```

@@

>>>>

plot.profit
```

@@

## Stratified effects in linearized fashion
```{r}

did2s(
      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )

did2s(
      data = df.size  %>% mutate(Size = Size / 1000 ), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * Size) + I(Tx * Size^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )
